### 2023-10-30 journal/algorithm.tex
editing space bounded version

\begin{figure*}
\begin{algorithmic}[1]
\setcounter{ALG@line}{39}
\Function{Block}{CreateBlock}{\typ{Node} \var{v}, \typ{int} \var{i}} \Comment{create new block $B$ for \op{Refresh} to install in \var{v}.\fld{blocks}[\var{i}]}
    \State \hangbox{let \var{B} be a new \typ{Block} with fields\label{initNewBlock}
    	\eleft\ \assign\ $\var{v}.\fld{left}.\head - 1$,\label{createEndLeft}
    	\eright\ \assign\ $\var{v}.\fld{right}.\head - 1$,\label{createEndRight}\\
		\fld{sum\sub{enq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{enq}} + \var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{enq}}\label{createSumEnq},\\
		\fld{sum\sub{deq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{deq}} + \var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{deq}}}\label{createSumDeq}
    \State \var{num\sub{enq}} \assign\ $\var{B}.\fld{sum\sub{enq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{enq}}$\label{computeNumEnq}
    \State \var{num\sub{deq}} \assign\ $\var{B}.\fld{sum\sub{deq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{deq}}$
    \If{$\var{v} = \var{root}$} \var{B}.\fld{size} \assign\ max(0, $\var{v}.\fld{blocks}[\var{i}-1].\size\ + \var{num\sub{enq}} - \var{num\sub{deq}}$)\label{computeLength}
    \EndIf
    \If{$\var{num\sub{enq}} + \var{num\sub{deq}} = 0$} \Return \nl \Comment{no blocks need to be propagated to \var{v}} \label{testEmpty} 
    \Else\ \Return \var{B}
    \EndIf
\EndFunction{CreateBlock}

@@

\Function{$\langle\typ{int}, \typ{int}\rangle$}{IndexDequeue}{\typ{Node} \var{v}, \typ{int} \var{b}, \typ{int} \var{i}} \com\ return $\langle\var{b}', \var{i}'\rangle$ such that \var{i}th dequeue in $D(\var{v}.\fld{blocks}[\var{b}])$
    \State \linecomment{is $(\var{i}')$th dequeue of $D(\var{root}.\fld{blocks}[\var{b}'])$}
    \State \linecomment{Precondition: $\var{v}.\fld{blocks}[\var{b}]$ is not \nl, was propagated to root, and contains at least \var{i} dequeues}
    \If{$\var{v} = \var{root}$} \Return $\langle\var{b, i}\rangle$ \label{indexBaseCase}
    \Else \Comment{First, find the superblock of $v.\fld{blocks}[b]$}
	    \State \fld{dir} \assign\ (\var{v}.\fld{parent.left} = \var{v} ? \fld{left} : \fld{right}) 
    	\State \var{sup} \assign\ \var{v}.\fld{blocks}[\var{b}].\fld{super}\label{idsup1}
	    \If{$\var{b} > \var{v}.\fld{parent.blocks}[\var{sup}].\fld{end\sub{dir}}$} \var{sup} \assign\ $\var{sup}+1$\label{supertest}\label{idsup2}
	    \EndIf\label{idsup3}
	    \State \linecomment{compute index \var{i} of dequeue in superblock}
	    \State \hangbox{\var{i} += $\var{v}.\fld{blocks}[\var{b}-1].\fld{sum\sub{deq}} -$ 
	    		$\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}-1].\edir].\fld{sum\sub{deq}}$}\label{computeISuperStart}
        \If{$\fld{dir} = \fld{right}$} 
        	\State \hangbox{\var{i} += $\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}].\eleft].\fld{sum\sub{deq}} - \mbox{ }$\\
					$\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}-1].\eleft].\fld{sum\sub{deq}}$}\label{considerLeftBeforeRight}
        \EndIf \label{computeISuperEnd}
        \State \Return\Call{IndexDequeue}{\var{v}.\fld{parent}, \var{sup}, \var{i}}
    \EndIf
\EndFunction{IndexDequeue}

>>>>

\begin{figure*}
\begin{algorithmic}[1]
\setcounter{ALG@line}{39}
\Function{Block}{CreateBlock}{\typ{Node} \var{v}, \typ{int} \var{i}} \Comment{create new block $B$ for \op{Refresh} to install in \var{v}.\fld{blocks}[\var{i}]}
    \State \hangbox{let \var{B} be a new \typ{Block} with fields\label{initNewBlock}
    	\eleft\ \assign\ $\var{v}.\fld{left}.\head - 1$,\label{createEndLeft}
    	\eright\ \assign\ $\var{v}.\fld{right}.\head - 1$,\label{createEndRight}\\
		\fld{sum\sub{enq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{enq}} + \var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{enq}}\label{createSumEnq},\\
		\fld{sum\sub{deq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{deq}} + \var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{deq}}}\label{createSumDeq}
    \State \var{num\sub{enq}} \assign\ $\var{B}.\fld{sum\sub{enq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{enq}}$\label{computeNumEnq}
    \State \var{num\sub{deq}} \assign\ $\var{B}.\fld{sum\sub{deq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{deq}}$
    \If{$\var{v} = \var{root}$} \var{B}.\fld{size} \assign\ max(0, $\var{v}.\fld{blocks}[\var{i}-1].\size\ + \var{num\sub{enq}} - \var{num\sub{deq}}$)\label{computeLength}
    \EndIf
    \If{$\var{num\sub{enq}} + \var{num\sub{deq}} = 0$} \Return \nl\ \Comment{no blocks need to be propagated to \var{v}}\label{testEmpty} 
    \Else\ \Return \var{B}
    \EndIf
\EndFunction{CreateBlock}

@@

\Function{$\langle\typ{int}, \typ{int}\rangle$}{IndexDequeue}{\typ{Node} \var{v}, \typ{int} \var{b}, \typ{int} \var{i}} 
    \State \linecomment{return $\langle\var{b}', \var{i}'\rangle$ such that \var{i}th dequeue in $D(\var{v}.\fld{blocks}[\var{b}])$ is $(\var{i}')$th dequeue of $D(\var{root}.\fld{blocks}[\var{b}'])$}
    \State \linecomment{Precondition: $\var{v}.\fld{blocks}[\var{b}]$ is not \nl, was propagated to root, and contains at least \var{i} dequeues}
    \If{$\var{v} = \var{root}$} \Return $\langle\var{b, i}\rangle$ \label{indexBaseCase}
    \Else \Comment{First, find the superblock of $v.\fld{blocks}[b]$}
	    \State \fld{dir} \assign\ (\var{v}.\fld{parent.left} = \var{v} ? \fld{left} : \fld{right}) 
    	\State \var{sup} \assign\ \var{v}.\fld{blocks}[\var{b}].\fld{super}\label{idsup1}
	    \If{$\var{b} > \var{v}.\fld{parent.blocks}[\var{sup}].\fld{end\sub{dir}}$} \var{sup} \assign\ $\var{sup}+1$\label{supertest}\label{idsup2}
	    \EndIf\label{idsup3}
	    \State \linecomment{compute index \var{i} of dequeue in superblock}
	    \State \hangbox{\var{i} += $\var{v}.\fld{blocks}[\var{b}-1].\fld{sum\sub{deq}} -$ 
	    		$\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}-1].\edir].\fld{sum\sub{deq}}$}\label{computeISuperStart}
        \If{$\fld{dir} = \fld{right}$} 
        	\State \hangbox{\var{i} += $\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}].\eleft].\fld{sum\sub{deq}} - \mbox{ }$\\
					$\var{v}.\fld{blocks}[\var{v}.\fld{parent.blocks}[\var{sup}-1].\eleft].\fld{sum\sub{deq}}$}\label{considerLeftBeforeRight}
        \EndIf \label{computeISuperEnd}
        \State \Return\Call{IndexDequeue}{\var{v}.\fld{parent}, \var{sup}, \var{i}}
    \EndIf
\EndFunction{IndexDequeue}
